---
title: "STA6235 Week 4"
author: "Your Name Here"
format: 
  html:
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
  error: true
editor: source
---

## Tuesday, September 12 (Happy Birthday Harper 🥳) 

1. From last week(s): pull in the [Palmer penguins dataset](https://allisonhorst.github.io/palmerpenguins/).

```{r}

```

2. Model penguin body mass (*body_mass_g*) as a function of species (*species*), flipper length (*flipper_length_mm*), bill length (*bill_length_mm*), and the interaction between flipper length and bill length. Remember to state the resulting regression model.

```{r}

```

3. Is the interaction significant? Remember to typeset the corresponding hypothesis test.

```{r}

```

4. Use the model stated in 2 to construct the following models:

- a model for gentoos with a bill length of 44 mm
- a model for chinstraps with a bill length of 44 mm
- a model for Adelies with a bill length of 44 mm

<!-- I am including the below to show you how to use the align* environment. 
     You can go into 09/12's lecture .qmd file to see how I typeset the example. -->
     
**Gentoos:**     
$$
\begin{align*}
\hat{y} &= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k
\end{align*}
$$

**Chinstraps:**     
$$
\begin{align*}
\hat{y} &= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k
\end{align*}
$$

**Adelies:**     
$$
\begin{align*}
\hat{y} &= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k
\end{align*}
$$

5. Use the simplified models in 4 to create the following predicted values

- `gentoo`: a value for gentoos with a bill length of 44 mm
- `chinstrap`: a value for chinstraps with a bill length of 44 mm
- `adelie`: a value for Adelies with a bill length of 44 mm

```{r}

```

6. Construct an appropriate data visualization utilizing the predicted values from 5.

<!-- Again, remember that you have my .qmd file for lecture;
     please take that code and edit it to what you need for homework! -->

```{r}

```

## Thursday, September 14

7. Model penguin body mass (*body_mass_g*) as a function of species (*species*), flipper length (*flipper_length_mm*), bill length (*bill_length_mm*), the interaction between flipper length and bill length, and the interaction between species and bill length. Remember to state the resulting regression model.

```{r}

```

8. Is the interaction between flipper length and bill length significant? Remember to typeset the corresponding hypothesis test.

```{r}

```

9. Is the interaction between species and bill length significant? Remember to typeset the corresponding hypothesis test.

```{r}

```

10. Use the model stated in 7 to construct the following models:

- a model for gentoos with a bill length of 44 mm
- a model for chinstraps with a bill length of 44 mm
- a model for Adelies with a bill length of 44 mm

<!-- I am including the below to show you how to use the align* environment. 
     You can go into 09/12's lecture .qmd file to see how I typeset the example. -->
     
**Gentoos:**     
$$
\begin{align*}
\hat{y} &= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k
\end{align*}
$$

**Chinstraps:**     
$$
\begin{align*}
\hat{y} &= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k
\end{align*}
$$

**Adelies:**     
$$
\begin{align*}
\hat{y} &= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k \\
&= \hat{\beta}_0 + ... + \hat{\beta}_k x_k
\end{align*}
$$

11. Use the simplified models in 4 to create the following predicted values

- `gentoo`: a value for gentoos with a bill length of 44 mm
- `chinstrap`: a value for chinstraps with a bill length of 44 mm
- `adelie`: a value for Adelies with a bill length of 44 mm

```{r}

```

12. Construct an appropriate data visualization utilizing the predicted values from 11.

<!-- Again, remember that you have my .qmd file for lecture;
     please take that code and edit it to what you need for homework! -->

```{r}

```

13. Perform model assumption checking and diagnostics. You should include statements (and R code backing up your statements) about the model assumptions, potential outliers, potential influential and leverage points, and multicollinearity. 

```{r}

```














